Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-03-11 response_to_review_SOLA-D-20-00015_v1.txt

Dear Editor,

Thank you very much for your email with the report on the first version of our manuscript ID SOLA-D-20-00015, titled "Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling".

We deeply acknowledge the reviewer, whose report reflects her/his very careful and interested read. All queries are very relevant, with useful and constructive criticisms and suggestions. Below, we copy/paste the full review. Following each query (Q) we include a corresponding answer (A), commenting the changes in the manuscript, in which all edited/new text is highlighted in red color font.

@@

-----------------------------------------------------------------------------------------
Q6. The abstract can be shortened somewhat, reducing the number of introductory sentences and with a little less emphasis on the method and future improvements, and more on the science results. In particular: the results of the energy balance analysis and the estimate of energy flux at the coronal base, which are important.

A6. We fully agree. We edited the Abstract, reducing the number of introductory lines from 12 down to 5, and greatly expanding the details in the results, while keeping the full abstract 2 lines shorter than in V1. The presentation of results is better organized now. We first summarize purely DEMT results. For this we were careful to mention which findings were first reported in previous DEMT studies. We still believe these are worth highlighting here as these were now found using the latest implementation of DEMT, in which we implemented here substantial improvements, as discussed in the draft. We close the abstract summarizing how the results of the latest implementation of AWSoM compare with DEMT, highlighting its shortcomings as well.

### 2020-03-11 lloveras_2020_v2.tex
Albert está trabajando en esto, no tocar todavía, gracias.

\begin{abstract}
\edit{We carry out a study of the global three-dimensional (3D) structure of the electron density and temperature of the quiescent inner solar corona ($r<1.25\,\mrsun$) by means of tomographic reconstructions and magnetohydrodynamic simulations. We use differential emission measure tomography (DEMT) and the Alfv\'en Wave Solar Model (AWSoM), in their latest versions. Two target rotations were selected from the solar minimum between solar cycles (SCs) 23 and 24 and the declining phase of SC 24. We report in quantitative detail on the 3D thermodynamic structure of the core and outer layers of the streamer belt, and of the high latitude coronal holes (CH), as revealed by the DEMT analysis. We report on the presence of two types of structures within the streamer belt, loops with temperature decreasing/increasing with height (dubbed down/up loops), as reported first in previous DEMT studies. We also estimate the heating energy flux required at the coronal base to keep these structures stable, found to be or order $10^5\,\erg\,\cminvs\,\s^{-1}$, consistently with previous DEMT and spectroscopic studies. Our findings may explained by Alfvén wave dissipation. We also compare the 3D DEMT and AWSoM results in distinct magnetic structures. We show that the agreement between the products of both techniques is the best so far, with an overall agreement $\lesssim 20\%$, depending on the target rotation and the specific coronal region. Even so, in its current version the ASWsoM model can not reproduce down loops. Also, the model exhibits a latitude variation of the electron density in the source region of the fast and slow components of the solar wind that differs from that of the DEMT results.}
\end{abstract}

@@

\edit{Non-tomographic studies of localized regions of the quiet-Sun corona have been carried out by means of DEM analysis. \citet{mackovjak_2014} used regularized inversion techniques to study characteristic temperatures in the quiet-Sun. \citet{lopez_2019} used a parametric method to study EUV dimmings after coronal mass ejections (CMEs) in order to estimate the coronal mass evacuated by the events. At a global scale, DEM analysis has been used by \citet{morgan_2017} to characterize the evolution of the temperature of the quiet-Sun corona during most of solar cycle (SC) 24.}

{The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global corona. {DEMT was first combined with a potential field source surface (PFSS) model by \citet{huang_2012} and \citet{nuevo_2013}. More recently,} \citet{lloveras_2017} combined DEMT with PFSS {models to study the thermodynamics of the global solar corona in specific magnetic structures for two target rotations selected from the last two solar minimum epochs. Also combining DEMT with a PFSS model,} \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux {required at the coronal base in order to maintain stable coronal loops}. In this article, {DEMT is first combined with the magnetic field of a magnetohydrodynamic (MHD) model.}

>>>>

\begin{abstract}
\edit{We carry out a study of the global three-dimensional (3D) structure of the electron density and temperature of the quiescent inner solar corona ($r<1.25\,\mrsun$) by means of tomographic reconstructions and magnetohydrodynamic simulations. We use differential emission measure tomography (DEMT) and the Alfv\'en Wave Solar Model (AWSoM), in their latest versions. Two target rotations were selected from the solar minimum between solar cycles (SCs) 23 and 24 and the declining phase of SC 24. We report in quantitative detail on the 3D thermodynamic structure of the core and outer layers of the streamer belt, and of the high latitude coronal holes (CH), as revealed by the DEMT analysis. We report on the presence of two types of structures within the streamer belt, loops with temperature decreasing/increasing with height (dubbed down/up loops), as reported first in previous DEMT studies. We also estimate the heating energy flux required at the coronal base to keep these structures stable, found to be or order $10^5\,\erg\,\cminvs\,\s^{-1}$, consistently with previous DEMT and spectroscopic studies. We discuss how these findings are consistent with coronal dissipation of Alfvén waves. We compare the 3D results of DEMT and AWSoM in distinct magnetic structures. We show that the agreement between the products of both techniques is the best so far, with an overall agreement $\lesssim 20\%$, depending on the target rotation and the specific coronal region. In its current implementation the ASWsoM model can not reproduce down loops though. Also, in the source region of the fast and slow components of the solar wind, the electron density of the AWSoM model increases with latitude, opposite to the trend observed in DEMT reconstructions.}
\end{abstract}

@@

\edit{Non-tomographic studies of localized regions of the quiet-Sun corona have been carried out by means of DEM analysis. \citet{mackovjak_2014} used regularized inversion techniques to study characteristic temperatures in the quiet-Sun. \citet{lopez_2019} used a parametric method to study EUV dimmings after coronal mass ejections (CMEs) to estimate the coronal mass evacuated by the events. At a global scale, DEM analysis has been used by \citet{morgan_2017} to characterize the evolution of the temperature of the quiet-Sun corona during most of solar cycle (SC) 24.}

{The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global corona. {DEMT was first combined with a potential field source surface (PFSS) model by \citet{huang_2012} and \citet{nuevo_2013}. More recently,} \citet{lloveras_2017} combined DEMT with PFSS {models to study the thermodynamics of the global solar corona in specific magnetic structures for two target rotations selected from the last two solar minimum epochs. Also combining DEMT with a PFSS model,} \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux {required at the coronal base to maintain stable coronal loops}. In this article, {DEMT is first combined with the magnetic field of a magnetohydrodynamic (MHD) model.}
